Community-Conditioned Language Models

### 2020-10-30 paper/paper.tex
couple of questions

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

We also note that the conditioned models perform differently across different communities---\
for some communities, the test perplexity of the conditioned models is a lot lowe, 
whereas for others it is the same or even slightly higher.
(TODO: talk about this in terms of mutual information instead?)
As an anecdotal observation, we note 
that communities where conditioning has the least effect
tend to be more organized around more ``general interest'' topics.
This makes sense intuitively, since communities with more niche topics
would tend to have more specialized vocabulary and speech patterns.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{todonotes}
\renewcommand{\UrlFont}{\ttfamily\small}

\newcommand\jp[1]{\todo[backgroundcolor=blue!10]{JP: #1}}

@@

We also note that the conditioned models perform differently across different communities---\
for some communities, the test perplexity of the conditioned models is a lot lower,\jp{Where can I see this?}
whereas for others it is the same or even slightly higher.
(TODO: talk about this in terms of mutual information instead?)
As an anecdotal observation, we note 
that communities where conditioning has the least effect
tend to be more organized around more ``general interest'' topics.\jp{Is there a way to quantify general interest topics? Community size in terms of number of users?}
This makes sense intuitively, since communities with more niche topics
would tend to have more specialized vocabulary and speech patterns.
